Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-19 paper/paper.tex
Add abstract #54 #56

>>>>

\begin{abstract}
This paper uses the satellite images of nighttime light to estimate economic growth rates in four unrecognized states of the former Soviet Union: Nagorno-Karabakh in Azerbaijan, Abkhazia and South Ossetia in Georgia, and Transnistria in Moldova. We then compare these estimates against those similarly obtained for parent states to gauge the impact of non-recognition as sovereign states on economic activities. The estimated economic growth rates do not differ much between the breakaway territories and their parent states, suggesting that the economic impact of non-recognition as states may be very limited.
\end{abstract}

\newpage
